### 2021-10-12 paper/pldi22/abstract.tex
Writing intro

\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in various fields. Recently,
  it rapidly evolved with a yearly release cadence and open development process
  to quickly adapt users’ demands to the language. In this fast-evolving nature
  of JavaScript, the need for \textit{language design assistants} has grown to
  understand original or revised semantics in the revision process correctly.
  Unfortunately, while several tools have been proposed as language design
  assistants for JavaScript in academia and industry, they should be manually
  updated to represent revised semantics every time. Besides, they lack the
  additional information for better comprehension of language semantics,
  including the relationship between specific semantics with conformance tests.

  To alleviate this problem, we present $\tool$, a \textit{live} language design
  assistant for JavaScript. It automatically synchronizes with a given language
  specification and shows related conformance tests in the revision process.
  Moreover, to better comprehend language semantics, we present a way to focus
  on specific semantics by automatically reducing semantics and filtering out
  conformance tests using user-defined \textit{syntactic views}, abstract syntax
  trees with abstracted nodes. In this paper, we conduct several case studies
  for JEDIT to demonstrate the effectiveness of live language design with
  syntactic views. Moreover, we experimentally show that syntactic views
  successfully reduce the \inred{XX.X}\% of semantics and filter out
  \inred{XX.X}\% of conformance tests on average using \inred{historically
  representative syntactic views}.
\end{abstract}

>>>>

\begin{abstract}\label{sec:abstract}
  JavaScript is a widely-used programming language in various fields. Recently,
  it has rapidly evolved with a yearly release cadence and open development
  process to adapt users' demands to the language quickly. In this fast-evolving
  nature of JavaScript, the need for \textit{language design assistants} has
  grown to understand original or revised semantics correctly in the revision
  process. Unfortunately, while several tools have been proposed as language
  design assistants for JavaScript in academia and industry, they should be
  manually updated to represent revised semantics every time. Besides, they lack
  information about the relationship between specific semantics with conformance
  tests.

  To alleviate this problem, we present $\tool$, a \textit{live} language design
  assistant for JavaScript, which automatically synchronizes with a given
  language specification and shows related conformance tests in the revision
  process. Moreover, to better comprehend language semantics, we present a way
  to focus on specific semantics by automatically reducing semantics and
  filtering out conformance tests using user-defined \textit{syntactic views},
  abstract syntax trees with abstracted nodes. In this paper, we conduct several
  case studies for $\tool$ with historical semantic updates to demonstrate the
  effectiveness of live language design with syntactic views. Moreover, we
  experimentally show that syntactic views successfully reduce the
  \inred{XX.X}\% of semantics and filter out \inred{XX.X}\% of conformance tests
  on average.
\end{abstract}

### 2021-10-12 paper/pldi22/intro.tex
Writing intro

\begin{itemize}
  \item \todo
\end{itemize}

>>>>

In the beginning, JavaScript was a scripting language designed in a ten-day
hack. However, it has become a de facto Web standard and eventually becomes one
of the dominating programming languages in various fields. For example, Node.js
introduced full-stack JavaScript by supporting server-side programming, and
JavaScript has recently begun to be used even in embedded systems and
microcontrollers for the Internet of Things (IoT). Furthermore, according to the
annual report of GitHub\footnote{\url{https://octoverse.github.com/}},
JavaScript has consistently been the most popular programming language based on
the number of contributors to GitHub projects.

Recently, JavaScript has rapidly evolved with a yearly release cadence and open
development process. In 2015, The Ecma Technical Committee 39 (TC39) decided to
annually release ECMAScript, the standard specification for JavaScript, with a
massive update in ECMAScript 2015 (ES6, 2015)~\cite{es6}. Moreover, they
published the specification as an open-source project in a GitHub repository to
quickly adapt users' demands to the language.

In this fast-evolving nature of JavaScript, the need for language design
assistants (LDAs)~\cite{lda} has grown to understand original or revised
semantics correctly in the revision process. Historically, researchers have
proposed several language design assistants, such as LISA~\cite{lisa} and
$\asfsdf$~\cite{asf-sdf, meta-env}, with semantics editors and the generators
for language-based tools, such as parsers, compilers, interpreters, and so on.
However, only small-size domain-specific languages are their targets due to
their low expressive power. On the other hand, there are several attempts to
develop language design assistants for JavaScript in the academy and industry.
For example, in the academy, \citet{jsexplain} presented JSExplain, a JavaScript
reference interpreter written in OCaml that closely follows ECMAScript and
produces execution traces for debugging both ECMAScript and a given program. In
the industry, Mozilla and several contributors introduced JavaScript
interpreters written in pure JavaScript, such as Narcissus~\cite{narcissus} and
engine262~\cite{engine262}, to aid the development of new features in
JavaScript.

However, existing language design assistants for JavaScript have two
limitations: \textit{manual updates} and \textit{lack of connection with
conformance tests}. First, all existing assistants are developed manually; thus,
developers should manually update them for each frequent evolution of
ECMAScript. This manual approach is a tedious, labor-intensive, and even
error-prone process. Moreover, they lack information about the relationship
between specific semantics with conformance tests. When a language designer
desires to understand specific language semantics, one possible approach is to
learn them from related conformance tests. Fortunately, TC39 provides Test262,
an official conformance test suite for the latest version of ECMAScript.
However, existing assistants do not utilize them to give a better comprehension
of language semantics.

In this paper, we present $\tool$, a \textit{live} language design assistant for
JavaScript, which automatically synchronizes with a given language specification
and shows related conformance tests in the revision process. To synchronize our
tool with ECMAScript, we utilize another tool $\jiset$~\cite{jiset}, which
automatically extracts a mechanized specification from a given version of
ECMAScript. Note that a specification is mechanized if and only if it is both
executable and formalized.
\todo
